---
title: "prediction assignment"
author: "Xiao"
date: "February 4, 2016"
output: html_document
---

In this project, my goalis to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants and predict the manner in which they did the exercise.

---
1.Download data and read in.
```{r, eval = FALSE}
# Download and read-in data.
urltraining<-("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
download.file(urltraining,"training.csv")
urltesting<-("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
download.file(urltesting,"testing.csv")
raindata <- read.csv("training.csv")
testdata <- read.csv("testing.csv")
```

2. Clean data 
```{r,eval=FALSE}
#Clean the testdata and remove NAs.
testvalid<-testdata[,colSums(is.na(testdata))!=nrow(testdata)]

#Keep "classe" variable
n <- c(names(testvalid),"classe")
my1 <- names(traindata) %in% n
train <- traindata[my1]
```
The new train and test set will only contain 60 valid variables.

3.Create data partition.
```{r,eval=FALSE}
library(caret)
set.seed(60)
inTrain <- createDataPartition(traindata$classe, list = FALSE,p=0.7)
training <- traindata[inTrain,]
testing <- traindata[-inTrain,]
```

4.I will train four model include:Random Forests,GBM, Tress and Linear.
```{r,eval=FALSE}
#Train several models to obtain accurary: fit1 Random Forests; fit2 GbM; fit3 Trees; fit4 linear;
set.seed(61)
 fit1 <- train(classe~., data=training, trControl = trainControl(method="repeatedcv") ,preProcess=c("center","scale","pca"),method="rf")
predt1 <- predict(fit1,testing)
confusionMatrix(predt1,reference=testing$classe)
set.seed(62)
fit2 <- train(classe~., data=training, trControl = trainControl(method="repeatedcv") ,preProcess=c("center","scale","pca"),method="gbm")
predt2 <- predict(fit2,testing)
confusionMatrix(predt2,reference=testing$classe)
set.seed(63)
fit3 <-train(classe~., data=training, trControl = trainControl(method="repeatedcv") ,preProcess=c("center","scale","pca"),method="rpart")
predt3 <- predict(fit3,testing)
confusionMatrix(predt3,reference=testing$classe)
set.seed(64)
fit4 <- train(classe~., data=training, trControl = trainControl(method="repeatedcv") ,preProcess=c("center","scale","pca"),method="lda")
predt4 <- predict(fit4,testing)
confusionMatrix(predt4,reference=testing$classe)
```
By cross-validation, the Accuracy of RF model is the highest with 0.9873 Accuracy. Then we choose Random Forests as our final model.
```{r,eval=FALSE}
predict(fit1,testvalid)
```

